Analysis of $\piup$-$\piup$ lattice QCD \\ scattering data

### 2015-03-18 Paper.tex
Add effective masses plot

The folded correlation functions with the fit functions are shown in
Figure~\ref{fig:folded}.

\begin{figure}[htbp]
    \centering
    \begin{minipage}[c]{0.49\linewidth}
        \centering
        \includegraphics[width=\linewidth]{plots/A100_24_L24_T48_beta190_mul0100_musig150_mudel190_kappa1632550__ev120__TB2_SO_LI6_new_c2_folded.pdf}
    \end{minipage}
    \hfill
    \begin{minipage}[c]{0.49\linewidth}
        \centering
        \includegraphics[width=\linewidth]{plots/A100_24_L24_T48_beta190_mul0100_musig150_mudel190_kappa1632550__ev120__TB2_SO_LI6_new_c4_folded.pdf}
    \end{minipage}
    \caption{%
        Folded correlation functions with cosh-like fit function. On the left
        side, the two point function is shown using a logarithmic ordinate
        scale. The four point function is shown on the right. Only the blue
        data points were used for fitting. The right ordinate shows the
        residuals in great magnification (red). One can see that the errors
        seem way too large compared to the residuals. This is a result of the
        autocorrelation of the data points.
    }
    \label{fig:folded}
\end{figure}

@@

The range of fitting was set manually by looking at the plateau of the
effective masses. This introduces some statistical errors which cannot be
quantified with the current machinery. A way to get beyond this limitation is
to run the whole analysis with all possible fit ranges. The different result
are then weighted by the $p$-values of the respective fit.

>>>>

In order to determine the fit range, I have used the effective mass as shown in
Figure~\ref{fig:m_eff}. The plateau starts at $t/a = 13$, so those are the
points I have used. The folded correlation functions with the fit functions are
shown in Figure~\ref{fig:folded}.

\begin{figure}[htbp]
    \centering
    \includegraphics[width=\linewidth]{plots/A100_24_L24_T48_beta190_mul0100_musig150_mudel190_kappa1632550__ev120__TB2_SO_LI6_new_c2_m_eff.pdf}
    \caption{%
        Effective mass of A100.24 ensemble.
    }
    \label{fig:m_eff}
\end{figure}

\begin{figure}[htbp]
    \centering
    \begin{minipage}[c]{0.49\linewidth}
        \centering
        \includegraphics[width=\linewidth]{plots/A100_24_L24_T48_beta190_mul0100_musig150_mudel190_kappa1632550__ev120__TB2_SO_LI6_new_c2_folded.pdf}
    \end{minipage}
    \hfill
    \begin{minipage}[c]{0.49\linewidth}
        \centering
        \includegraphics[width=\linewidth]{plots/A100_24_L24_T48_beta190_mul0100_musig150_mudel190_kappa1632550__ev120__TB2_SO_LI6_new_c4_folded.pdf}
    \end{minipage}
    \caption{%
        Folded correlation functions with cosh-like fit function. On the left
        side, the two point function is shown using a logarithmic ordinate
        scale. The four point function is shown on the right. Only the blue
        data points were used for fitting. The right ordinate shows the
        residuals in great magnification (red). One can see that the errors
        seem way too large compared to the residuals. This is a result of the
        autocorrelation of the data points. Ensemble is A100.24.
    }
    \label{fig:folded}
\end{figure}

@@

The range of fitting was set manually by looking at the plateau of the
effective masses (see Figure~\ref{fig:m_eff}). This introduces some statistical
errors which cannot be quantified with the current machinery. A way to get
beyond this limitation is to run the whole analysis with all possible fit
ranges. The different result are then weighted by the $p$-values of the
respective fit.
